---
title: "Shiny Application and Reproducible Pitch"
author: "tishita goel"
date: "25/11/2021"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Goal

There are two components to this peer-reviewed assignment. You'll start by building a Shiny application and deploying it to Rstudio's servers. Second, you'll create a reproducible pitch presentation for your application using Slidify or Rstudio Presenter.

## Steps to Perform

1. Create a shiny application and accompanying documentation. The documentation should be viewed as everything a user will need to get up and running with your programme.
2. Use Rstudio's shiny server to deploy the app.
3. Paste the app's link into the given text box to share it.
4. Share your server.R and ui.R codes on github

## How to use the application

We design a linear model to predict a child's height based on the gender and average height of the parents using data from the Galton Families dataset.

The application is running on (https://tishitagoel.shinyapps.io/Reproducible_Pitch/)

ui.R, and Server.R Code in my github repository (https://github.com/tishitagoel/DDP-Week-4)

## Plot
```{r plot,warning=FALSE}
library(HistData)
##The GaltonFamilies dataset provided the data for the app. 
data(GaltonFamilies)
library(HistData)
data(GaltonFamilies)
plot(jitter(GaltonFamilies$childHeight) ~ GaltonFamilies$midparentHeight,xlab="Average Height of the Parents (in inches)",ylab="Height of the Child (in inches)",main="Scatterplot of Galton Family Data",pch=19,frame.plot=FALSE,col=ifelse(GaltonFamilies$gender=="female", "pink", "light blue"))
legend(65,80,pch=c(19,19),col=c("pink","light blue"),c("female", "male"),bty="o",cex=.8)
```
